\huge Tor's Usability for Censorship Circumvention

### 2016-04-15 pets2017-paper/pets2017-paper.tex
Define a \pquote macro for formatting participant quotes.

@@

\begin{quotation}
\noindent P2:\textit{"I don't know what any of those means (list of bridges),or what that (proxy)
 means at all."}\\

 \noindent P3:\textit{``The vocabulary is really challenging, for someone not doing IT work.''}\\

 \noindent P4:\textit{``I didn't know why I was getting back `establishing encrypted directory'--what does that mean?''}\\
\end{quotation} 
The text in the interface intended to guide users through the process was not understood by our participants. The text also gave our participants a sense that the process intimidating for people who did not have a technical background.

@@

Participants across all censorship environments connected directly to the Tor network. When they did, they did so because they were taking the path of least resistance first or intimidated by the configuration process. 
\begin{quotation}
\noindent P9: \textit{``Configure seemed manual, so I clicked connect.''}\\

\noindent P14:\textit{``The words were confusing. I don't really understand computers. I don't know what configure means in this setting. Hmm, is it going to crash? When you see connect, you want to click it because you really want it to connect.''} 
\end{quotation}

@@

\begin{quotation}
\noindent P10: \textit{``I was censored, so I picked the configure.''}
\end{quotation}

@@

\begin{quotation}
\noindent P7:\textit{``The bridge screen was the most challenging. It seemed very technical to me. I don't know what a bridge is.''}\\

\noindent P12:\textit{``I decided which options to choose by process of elimination with trial and error.''}
\end{quotation}

@@

\begin{quotation} 
\noindent P8:\textit{``I have no clue what's the difference between flashpoxy, fte, etc. I need to know why the built-in ones aren't working. And why do I need a custom bridge if there are options built in?'}\\

\noindent P7:\textit{``Since it (obfs3) said recommended, it helped actually, and I selected it because it was chosen. I saw the custom bridges option, but I didn't know what to enter there so I went with this (obfs3).''}
\end{quotation}

@@

\begin{quotation}
\noindent P4:\textit{``When I saw obfs3 as the recommended option, the next option logically for me was obfs4.''}\\

\noindent P5:\textit{``I tried the pluggable transport that used google, because I noticed that google was working (when I was using a non-Tor browser).''}
\end{quotation}

@@

\begin{quotation}
\noindent P11:\textit{``I think you can only answer this question (does this computer need a local proxy) if you know what a local proxy is. Otherwise, you have no chance..''}
\end{quotation}

@@

\begin{quotation}
\noindent P15:\textit{``I didn't know if this computer had any proxy information. I wasn't able to find it if it did.''}
\end{quotation}

@@

\begin{quotation}
\noindent P16:\textit{``There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.''}\\

\noindent P6:\textit{``How long does this actually take (to connect)? This took way too long, and I didn't know how long it should take.''}

\noindent P1:\textit{``It was hard to figure out if the progress bar wasn't moving because the connection was censored, or if it was just slow.''}
\end{quotation}

>>>>

% Format a participant quotation. It should be inside a quotation environment.
\newcommand{\pquote}[2]{
\begin{quotation}
\noindent #1:~\textit{``#2''}
\end{quotation}
}

@@

\pquote{P2}{I don't know what any of those means (list of bridges),or what that (proxy) means at all.}
\pquote{P3}{The vocabulary is really challenging, for someone not doing IT work.}
\pquote{P4}{I didn't know why I was getting back `establishing encrypted directory'---what does that mean?}
The text in the interface intended to guide users through the process was not understood by our participants. The text also gave our participants a sense that the process intimidating for people who did not have a technical background.

@@

Participants across all censorship environments connected directly to the Tor network. When they did, they did so because they were taking the path of least resistance first or intimidated by the configuration process. 
\pquote{P9}{Configure seemed manual, so I clicked connect.}
\pquote{P14}{The words were confusing. I don't really understand computers. I don't know what configure means in this setting. Hmm, is it going to crash? When you see connect, you want to click it because you really want it to connect.}

@@

\pquote{P10}{I was censored, so I picked the configure.}

@@

\pquote{P7}{The bridge screen was the most challenging. It seemed very technical to me. I don't know what a bridge is.}
\pquote{P12}{I decided which options to choose by process of elimination with trial and error.}

@@

\pquote{P8}{I have no clue what's the difference between flashpoxy, fte, etc. I need to know why the built-in ones aren't working. And why do I need a custom bridge if there are options built in?}
\pquote{P7}{Since it (obfs3) said recommended, it helped actually, and I selected it because it was chosen. I saw the custom bridges option, but I didn't know what to enter there so I went with this (obfs3).}

@@

\pquote{P4}{When I saw obfs3 as the recommended option, the next option logically for me was obfs4.}
\pquote{P5}{I tried the pluggable transport that used google, because I noticed that google was working (when I was using a non-Tor browser).}

@@

\pquote{P11}{I think you can only answer this question (does this computer need a local proxy) if you know what a local proxy is. Otherwise, you have no chance..}

@@

\pquote{P15}{I didn't know if this computer had any proxy information. I wasn't able to find it if it did.}

@@

\pquote{P16}{There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.}
\pquote{P6}{How long does this actually take (to connect)? This took way too long, and I didn't know how long it should take.}
\pquote{P1}{It was hard to figure out if the progress bar wasn't moving because the connection was censored, or if it was just slow.}
